Latentcor: An R Package for Latent Correlation Estimation

### 2021-05-18 paper/paper.Rmd
Create JOSS paper folder

---
title: "paper"
author: "Mingze Huang, Irina Gaynanova, Christian L. Muller"
date: "5/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
# Example from https://joss.readthedocs.io/en/latest/submitting.html
title: 'Latentcor: An R Package for Latent Correlation Estimation'
tags:
  - R
  - Statistics
  - Latent Correlation
authors:
  - name: Mingze Huang
    orcid: 0000-0003-3919-1564
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Irina Gaynanova
    orcid: 0000-0000-0000-0000
    affiliation: 2
  - name: Christian L. Muller
affiliations:
 - name: Department of Statistics, Texas A& M University
   index: 1
 - name: Department of Economics, Texas A& M University
   index: 2
 - name: Department of Statistics, University of Munich
   index: 3
date: 18 May 2021
year: 2021
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

# Summary

# Mathematics

# Citations

# Rendered R Figures

# Acknowledgements

# References
